
\section*{Acknowledgment}


We have used at one point ``ChatGPT'' to improve upon the grammar of selected sections with the question: ``Improve the grammar of ...''. However, we stopped that practice early on due to wrong corrections, and have used Grammarly throughout the paper.

% UVA
The work was in part sponsored by NSF Grant \#2346173 and \# 2303700, POSE: Phase II: MLCommons Research for Science: Enabling Open-Source Ecosystems for Scientific Foundation Models by Community Standards and Benchmarks

% Wisconsin ACKs
The portion of this work done at UW-Madison is supported in part by NSF grant CNS-2312688 and by the U.S. Department of Energy, Office of Science, Office of Advanced Scientific Computing Research, under Award Number DE-SC-0026036.

% Fermi (Ben & Nhan) Acks
This manuscript has been in part authored by FermiForward Discovery Group, LLC under Contract No. 89243024CSC000002 with the U.S. Department of Energy, Office of Science, Office of High Energy Physics.
Fermilab Report Number FERMILAB-PUB-25-0835-CSAID. 

This work was supported by DOE ASCR Microelectronics Science Research Center Projects, BIA.  This material is based upon work supported by the U.S. Department of Energy, Office of Science, under contract number DE-AC02-06CH11357.

This research was in part sponsored in part by and used resources of the Oak Ridge Leadership Computing Facility (OLCF), which is a DOE Office of Science User Facility at the Oak Ridge National Laboratory (ORNL) supported by the U.S. Department of Energy under Contract No. DE-AC05-00OR22725.

Shirley Moore's work on this paper was supported by the Department of Energy Office of Science under award \#DE-SC0024352.

Kirkpatrick's work was made possible through the National Science Foundation award \#2226453.

This research was funded in part by and used resources at the Argonne Leadership Computing Facility, which is a DOE Office of Science User Facility supported under Contract DE-AC02-06CH11357.

Research was sponsored by the Department of the Air Force Artificial
Intelligence Accelerator and was accomplished under Cooperative
Agreement Number FA8750-19-2-1000. The views and conclusions contained
in this document are those of the authors and should not be interpreted
as representing the official policies, either expressed or implied, of
the Department of the Air Force or the U.S.\ Government.
The U.S.\ Government is authorized to reproduce and distribute reprints
for Government purposes notwithstanding any copyright notation herein.

Gary Mazzaferro has participated in discussions as part of the working group meetings surrounding benchmark definitions and applicability. 