\section*{Appendix A. Abbreviations}
\label{sec:abbrev}

\begin{description}

\item[$\bf A, P$] Application and Parameters – Formal components defining a scientific task $T = (A, P)$.
\item[AI] Artificial Intelligence – Computational systems performing tasks that typically require human intelligence, such as learning, reasoning, or perception.
\item[API] Application Programming Interface – A set of functions and protocols for building and integrating software applications.
\item[ARC] AI2 Reasoning Challenge – Benchmark for commonsense and science question answering at the K–12 level.
\item[AristoBench] A benchmark based on U.S. science exam questions.
\item[$\bf B$] Benchmark – A formal specification of an evaluation setup $B = (I, D, T, M, C_B, R)$.
\item[BioASQ] A benchmark for biomedical question answering and document retrieval.
\item[BSP] Bulk synchronous programming
\item[CAPEX/OPEX] Capital Expenditure / Operating Expenditure – Financial measures of investment and operational costs.
\item[CarbonTracker] Tool for tracking and reporting ML training energy use and CO$_2$ emissions.
\item[$\bf C_B$, $C_c$] Benchmark and Component Constraints – Rules applied to benchmarks or components for fairness, reproducibility, and comparability.
\item[CodeCarbon] Python package estimating CO$_2$ emissions based on compute energy and grid intensity.
\item[CO$_2$e] Carbon Dioxide Equivalent – Standardized unit comparing greenhouse gas emissions by global warming potential.
\item[cPUE] Compute-Only Power Usage Effectiveness – Refinement of PUE focusing on compute power versus total facility power.
\item[CORE-Bench] A benchmark for computational reproducibility.
\item[CPU] Central Processing Unit – The main processor of a computer, optimized for sequential execution.
\item[CSR] Corporate Social Responsibility – A framework for a company’s environmental and social accountability.
\item[Data Carpentry] A Carpentries initiative focused on teaching data management and analysis skills.
\item[DCGM] Data-Centre GPU Manager – NVIDIA’s toolkit for GPU monitoring, management, and power measurement.
\item[DCiE] Data-Centre-infrastructure Efficiency – Metric defined as $P_{\mathrm{IT}} / P_{\mathrm{fac}}$, the reciprocal of PUE.
\item[DeepONet] Deep Operator Network – A neural architecture for learning operators mapping between function spaces.
\item[DOE] U.S. Department of Energy – Federal agency supporting large-scale AI and HPC research.
\item[DOI] Digital Object Identifier – Persistent identifier for published datasets, software, and benchmarks.
\item[DVFS] Dynamic Voltage and Frequency Scaling – Power management technique adjusting CPU/GPU frequency to balance performance and energy.
\item[EDP] Energy–Delay Product – A metric combining performance (time-to-solution) and energy efficiency.
\item[EIA] Energy Information Administration – U.S. agency providing official energy statistics and analysis.
\item[EE-HPC WG] Energy Efficient HPC Working Group – Community standardizing energy measurement and reporting in HPC.
\item[ElectricityMap] API providing real-time carbon intensity of electricity grids worldwide.
\item[Energy-to-Solution] Total energy consumed to complete a computational task.
\item[EU] European Union – Political and economic union of 27 member states.
\item[FAIR] Findable, Accessible, Interoperable, Re-usable – Principles for data and software management.
\item[FNO] Fourier Neural Operator – Deep learning architecture for solving partial differential equations efficiently.
\item[Galactica Eval] A benchmark measuring scientific writing and knowledge recall capabilities.
\item[GFLOPS] Giga Floating-Point Operations per Second – Measure of computational performance.
\item[GFLOPS/W] GFLOPS per Watt – Energy efficiency metric used in Green500.
\item[GPU] Graphics Processing Unit – Specialized processor for graphics and parallel computation, widely used in ML and HPC.
\item[Green500] Ranking of the most energy-efficient supercomputers in the world.
\item[HPC] High-Performance Computing – The use of supercomputers and parallel processing to solve large, complex problems.
\item[HPC AI500] Benchmark suite evaluating deep learning performance at HPC scale.
\item[HPC Carpentry] Carpentry modules teaching HPC skills and workflows.
\item[HPCG] High Performance Conjugate Gradients --- a benchmark that
represents real-world scientific workloads, such as partial
differential equations' solvers, better than the LINPACK benchmark.
\item[HPCG-Power] Energy-aware version of the HPCG benchmark.
\item[HPL] High-Performance LINPACK Benchmark – Measures floating-point computing power.
\item[HPL-MxP] Mixed-Precision variant of the LINPACK benchmark that
uses multiple floating-point formats for improved FLOP and energy metrics.
\item[IO500] Benchmark suite evaluating HPC storage performance.
\item[IOPS] Input/Output Operations Per Second – Metric measuring storage system performance.
\item[$\bf I$] Infrastructure – Hardware and software environment required to execute a benchmark.
\item[$\bf J/epoch$] Joules per training epoch – ML training energy efficiency metric.
\item[$\bf J/sample$] Joules per sample – Energy consumed per inference or training sample.
\item[$\bf J/step$] Joules per simulation step – Energy metric for iterative simulation workloads.
\item[JouleSort] Benchmark measuring energy efficiency of sorting tasks.
\item[Kaggle] Online platform hosting AI and data science competitions.
\item[Kepler] Kubernetes-based Efficient Power Level Exporter – Collects power metrics in containerized workloads.
\item[KPI] Key Performance Indicator – Quantitative metric for performance or efficiency.
\item[kg CO$_2$e] Kilograms of CO₂ equivalent – Emission unit measuring carbon footprint.
\item[kg CO$_2$e/job] Kilograms CO₂e emitted per completed computational job.
\item[$kWh$] Kilowatt-hour – Standard unit of electrical energy.
\item[LAB-Bench] Benchmark evaluating AI models on laboratory research assistance tasks.
\item[LLM] Large Language Model – AI model trained on massive text corpora, capable of natural language generation.
\item[ML] Machine Learning – A subset of AI focused on algorithms that improve automatically through data.
\item[MLCommons] Open engineering consortium developing ML benchmarks, datasets, and best practices.
\item[MLflow] Open-source platform for managing the ML lifecycle, including experimentation and deployment.
\item[MLPerf] MLCommons benchmark suite for ML training and inference performance.
\item[MLPerf HPC] MLPerf extension for measuring ML workloads in HPC environments.
\item[MLPerf Power] MLPerf extension tracking energy efficiency (e.g., Joules/sample).
\item[MLPerf Tiny Power] MLPerf subset focused on energy use in constrained edge devices.
\item[MMLU] Massive Multitask Language Understanding benchmark – Evaluates cross-domain academic knowledge.
\item[MPI] Message Passing Interface – Communication standard for parallel programming in distributed-memory systems.
\item[M] Metrics – Quantitative measures such as accuracy, throughput, latency, or energy.
\item[NVML] NVIDIA Management Library – API for monitoring and managing NVIDIA GPU performance and power.
\item[OmniStat] AMD’s monitoring and management interface, similar to NVIDIA’s NVML.

\item [$P_{fac}$]  Facility Power

\item [$P_{IT}$] IT Equipment Power

\item[PDEBench] Benchmark for solving partial differential equations using ML and operator learning.
\item[PM\_COUNTER] Node-level power counter (e.g., HPE-Cray) for system-level power tracking.
\item[PowerAPI] Software library and framework for energy measurement and analysis.
\item[PPA] Power-Purchase Agreement – Contract defining terms for renewable energy procurement.
\item[PUE] Power Usage Effectiveness – Data center efficiency metric $P_{\mathrm{fac}} / P_{\mathrm{IT}}$.
\item[PTDaemon] SPEC Power Temperature Daemon – Tool for calibrated power measurement in benchmarks.
\item[PyTorch Profiler] Tool for performance analysis of PyTorch models.
\item[QA] Question Answering – NLP task where systems respond to questions posed in natural language.
\item[R] Programming language for statistical computing and data analysis.
\item[RAPL] Running Average Power Limit – Intel/AMD interface for on-chip power measurement.
\item[RFP] Request for Proposal – Formal request soliciting project bids or benchmark implementations.
\item[$R$] Results – Outputs of a benchmark including accuracy, energy, and performance metrics.
\item[SCIQ] Science Question Answering benchmark focusing on inference and reasoning.
\item[SciEval] Benchmark for multi-domain scientific reasoning.
\item[SciSafeEval] Benchmark measuring safety alignment of AI systems in scientific contexts.
\item[Scaphandre] Open-source energy monitoring agent integrating with Prometheus.
\item[SERT] Server Efficiency Rating Tool – SPEC benchmark for server energy efficiency.
\item[Slurm] Simple Linux Utility for Resource Management – Widely used HPC workload manager.
\item[SM] Streaming Multiprocessor – GPU core building block for parallel computation.
\item[SME] Small and Medium-sized Enterprise – Business classification by size and revenue.
\item[Software Carpentry] Community teaching foundational computing skills for researchers.
\item[SKU] Stock-Keeping Unit
\item[SPEC] Standard Performance Evaluation Corporation – Organization developing performance benchmarks.
\item[SPEC HPC] SPEC benchmark suite for HPC system performance.
\item[SPECpower] SPEC benchmark suite measuring server energy efficiency.
\item[SQL] Structured Query Language – Standard for managing and querying relational databases.
\item[STREAM] Synthetic benchmark measuring sustainable memory bandwidth.
\item[$T$] Scientific Task – Core task evaluated by a benchmark, e.g., classification or prediction.
\item[TDP] Thermal Design Power – Maximum heat generated by a processor under typical workloads.
\item[TensorBoard] Visualization toolkit for TensorFlow training and profiling.
\item[TorchInfo] Python package summarizing PyTorch models (layers, parameters, memory use).
\item[TOP500] Official list of the 500 most powerful supercomputers in the world.
\item[TPC-Energy] Benchmark suite for transaction workloads with energy measurement.
\item[TVA] Tennessee Valley Authority – U.S. regional energy provider supporting grid research.
\item[Vampir] Performance analysis tool for parallel applications with detailed execution tracing.
\item[VTune] Intel VTune Profiler – Performance and energy analysis tool for fine-grained profiling.
\item[WattTime] API providing marginal emissions signals for carbon-aware workload scheduling.
\item[Wh/DB-phase] Watt-hours per database phase – Metric used in TPC-Energy benchmarks.

\end{description}


