\section*{Appendix B. Contributions}
\label{sec:contrib}

\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}


\newcommand{\AUTHOR}[2]{%
    \item \textbf{%
        \ifthenelse{\equal{#2}{notified}}%
            {\parindent0pt #1}%
            {\textcolor{red}{x #1}}%
    }%
}


\begin{itemize}[label={}, leftmargin=0pt]
    
\AUTHOR{Gregor von Laszewski}{notified} is the lead author of the paper. He identified first that efforts in benchmark carpentry and democratization are needed. He has lead the organization of this paper in the MLCommons Science Working Group. He also created the initial version of \cite{www-las-mlcommons-benchmark-coolection} which is related and relevant to this effort.

\AUTHOR{Piotr Luszczek}{notified} has contributed to integration of many
decades of experiences from designing, implementing, running, and
collecting results from HPC benchmarks.

\AUTHOR{Wesley Brewer}{notified} has contributed to the simulation section.

\AUTHOR{Jeyan Thiyagalingam}{notified} has worked on the GPU benchmarking section. Reviewed the paper and made corrections.

\AUTHOR{Juri Papay}{notified} has worked on  the GPU benchmarking section. Updated the GPU HW details of MLCommon benchmarks.

\AUTHOR{Geoffrey C. Fox}{notified} is leading the MLCommons Science Working group and has contributed to many of the ideas. The experiences and discussions with Gregor von Laszewski around improvements to the earthquake benchmark have significantly contributed to this effort. The educational effort of using the earthquake benchmark with a number of students motivated this effort.

\AUTHOR{Armstrong Foundjem}{notified} has provided an early version and led the Energy section, and has contributed to the paper writing and overall improvement.

\AUTHOR{Gregg Barrett}{notified} has participated in discussions as part of the working group meetings and contributed to an early version of this paper.

\AUTHOR{Murali Emani}{notified} has participated in discussions as part of the working group meetings and improved the article.

\AUTHOR{Shirley V. Moore}{notified} has written text for the Profiling and Performance Analysis Section. 

%Geoffrey said to add
\AUTHOR{Vijay Janapa Reddi}{notified} has participated in discussions as part of the working group meetings and improved the article.

\AUTHOR{Matthew D. Sinclair, Shivaram Venkataraman and Rutwik Jain} {notified} participated in discussions as part of the working group meetings and wrote the variability section of the article. Sinclair also wrote the simulation section of the paper and helped improve the paper in other sections.

\AUTHOR{Christine Kirkpatrick}{notified} has worked on conceptualizing the ideas and discussion, and helping with the Carpentries background section.

\AUTHOR{Kartik Mathur}{notified} Has worked on improving an early version of the Energy section.

\AUTHOR{Victor Lu}{notified} Has participated in writing the paper.

\AUTHOR{Tianhao Li}{notified} has participated in discussions as part of the working group meetings and participated in identification of limitations of current benchmarks.

\AUTHOR{Sebastian Lobentanzer}{notified} 
Has participated in the discussions in the working group and has contributed to the abstract, intro, definitions, formalization, and benchmark sections with content and editing.

\AUTHOR{Sujata Goswami}{notified} has worked on the MLCommons benchmark details in Table \ref{tab:benchmarks-mlcommons}.

\AUTHOR{Abdulkareem Alsudais}{notified} has reviewed the motivation to AI Benchmark Carpentry and contributed to the writing of this paper.

\AUTHOR{Kongtao Chen}{notified} has worked on the monitoring sections, related benchmarks, and participated in discussions as part of the working group meetings.

\AUTHOR{Tejinder Singh}{notified} has edited and improved AI hardware benchmarking and infrastructure sections and provided new KPIs for AI hardware benchmarking. 

\AUTHOR{Kirsten Morehouse
knmorehouse@gmail.com}{notified} has participated in discussions as part of the working group meetings. Morehouse also reviewed
the paper and made improvements.

\AUTHOR{Marco Colombo, Benjamin Hawks, and Nhan Tran}{notified} have worked on the benchmark ontology and Table \ref{tab:ontology}.

\AUTHOR{Khojasteh Z. Mirza}{notified} has participated in discussions as part of the working group meetings and worked an a very early version of the energy section.

\AUTHOR{Renato Umeton}{notified}
revised the manuscript for consistency and coherence.

\AUTHOR{Sasidhar Kunapuli and Gavin Farrell
gavinmichael.farrell@phd.unipd.it}{notified} have participated in discussions as part of the working group meetings.


\end{itemize}
